---
title: "Behavioural Analysis Tacit Coordination"
author: "Katerina Christodoulou"
date: "2/22/2021"
output:
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Preperation: Preperation of the WD, the packages-to-use and the data. 

### Directory
```{r}
# Clear R enviroment
rm(list=ls())

# Set working directory
setwd("C:/Users/katec/Desktop/Major_Project/5. Analysis/Behavioural")

```

### Loaded Libraries

```{r echo=TRUE}
library(data.table)
library(tidyverse)
library(ggplot2)
library(psych)
library(plotfunctions)
library(plyr); library(dplyr)
#library(cowplot) #for manuscript ready figures ????????????????????????

library(lme4)
library(lmerTest)# to get p-value estimations that are not part of the standard lme4 packages
library(emmeans)
library(Hmisc) 
library(mltools)

library(sjPlot) #for plotting lmer and glmer mods
library(sjmisc) 
library(effects)
library(sjstats) #use for r2 functions

library(ggeffects) #plotting glmer probabilities
library(magrittr)
library(splines)

```

### Data Importation


```{r data_all, eval = TRUE, echo=FALSE}
data_all <- NULL
files<- list.files(pattern = "*.csv")
for (i in 1:length(files)) {
  # assign selected columns from the read file in the file list to a temp variable
  tmp <- assign(files[i], select(as.data.table(fread(files[i])), subject_nr,load_condition, 
                                 stim_type, fully_correct, any_correct, 
                                 semi_correct, correct, image_set, image_num_p1_resp_1, 
                                 image_num_p2_resp_1))
  tmp$trial <- 1:nrow(tmp)
  n_trials <- nrow(tmp)/2
  tmp$block <- ifelse(as.numeric(rownames(tmp)) < (n_trials+1), "1", "2")
  
  data_all <- rbind(data_all,tmp)
}


data_all[, stim_type := as.factor(stim_type)] # in dt chr are not by default converted into factors
data_all[, load_condition := as.factor(load_condition)] 
data_all[, block := as.factor(block)] 
data_all[, correct := as.numeric(correct)] 

```


## Exploring the Data

Explore the data for missing values & visually display it to understand what is in the dataset and what characteristics may the data exhibit.

#### Missing Values

```{r}

which(!complete.cases(data_all))

```
[x] There appears to be no missing values


#### Descriptives

##### Define function for SE
```{r}

se <- function(x) sqrt(var(x)/length(x))

```


##### Mean matching accuracy by stimulus type & by load condition

Get the mean accuracy of each condition to get a rough idea of the data & conditions
(*practicing on 3 different ways*)

```{r}
subdat_s <- aggregate(correct ~ stim_type,
          data_all,
          mean)
subdat_l <- aggregate(correct ~ load_condition,
          data_all,
          mean)
subdat <- cbind(subdat_l, subdat_s)
```


Alternative(a):

```{r}
# Get the mean & standard deviation of mean accuracy by each condition

sub_dat <- data.table(data_all)[,.(stim_type, load_condition, correct)]
sub_dat[,`:=`(mean_corr = round(mean(correct),2), sd_corr= round(sd(correct),2)), by= .(stim_type, load_condition)]
sub_dat[,correct:=NULL]
descr_data<- sub_dat %>% distinct(mean_corr, .keep_all = TRUE)
```
Alternative(b):
```{r}
descr_data2 <- ddply(data_all,  c("load_condition", "stim_type"), summarise,
                mean_corr = round(mean(correct),2), sd_corr = round(sd(correct),2), 
                se_corr = round(se(correct), 2))
```


##### Mean matching accuracy by stimulus type, load condition and **block**

```{r}
descr_data3<- ddply(data_all,  c("load_condition", "stim_type", "block"), summarise,
                mean_corr = round(mean(correct),2), 
                sd_corr = round(sd(correct),2), 
                se_correct = round(se(correct), 2))

descr_data3.df<- as.data.frame(descr_data3)


```


### Visualisations of the data

#### Plotting mean accuracy by stimulus type and load condition

Base Plot 1: barplot of x = stim_type, y= coord_idx, fill= load

```{r}
base_plot <- ggplot(data=descr_data2,
                    aes(x=stim_type, y=mean_corr, fill=load_condition)) +
  geom_bar(stat="identity", position= position_dodge(), width= 0.9) +
  geom_errorbar(aes(ymin = mean_corr-se_corr, ymax = mean_corr+se_corr),  
                width=.5, position=position_dodge(0.9)) + # weird error bars
  geom_text(aes(label= mean_corr), color = "white", position = position_dodge(1), size=3.5)+
  scale_fill_brewer(palette="Set1")+
  xlab('Stimulus Type') +
  ylab('Coordination Index')+
  labs(fill='Load condition') +
  ggtitle("Mean coordination performance by condition")+
  coord_cartesian(ylim=c(0.0, 1))+
  theme_minimal()

base_plot

```

Base Plot 2: barplot of x = load, y= coord_idx, fill= stim_type

```{r}
base_plot2 <- ggplot(data=descr_data2,
                    aes(x=load_condition, y= mean_corr, fill=stim_type)) +
  geom_bar(stat="identity", position= position_dodge(), width= 0.9) +
  geom_errorbar(aes(ymin = mean_corr-se_corr, ymax = mean_corr+se_corr),  
                width=.5, position=position_dodge(0.9))+
  geom_text(aes(label= mean_corr), color = "white", position = position_dodge(1), size=3.5)+
  scale_fill_brewer(palette="Set1")+
  xlab('Load Condition') +
  ylab('Coordination Index')+
  labs(fill='Stimulus Type') +
  ggtitle("Mean coordination performance by condition")+
  theme_minimal()+
  coord_cartesian(ylim=c(0.0, 1))
  
  
  
base_plot2

```

#### Plotting mean accuracy in two blocks by condition

```{r}
# data preperation
base3 <- tidyr::unite(descr_data3.df,"st_lc",stim_type,load_condition,remove = T)

# plot
base_plot3 <- ggplot(data=base3,
                     aes(x=block, y= mean_corr, fill=st_lc)) +
  geom_bar(stat="identity", position= position_dodge( width= 0.9)) +
  # geom_errorbar(aes(ymin = mean_corr-se_corr, ymax = mean_corr+se_corr),  
                # width=.5, position=position_dodge(0.9)) +
  geom_text(aes(label= mean_corr), color = "white", position = position_dodge(1), size=3.5)+
  scale_fill_brewer(palette="Set1")+
  labs(title = paste("Mean coordination performance \n between blocks per condition"), x = 'Block',
y = 'Coordination Index')+
  labs(fill='Condition') +
   coord_cartesian(ylim=c(0.0, 1))+
   theme_minimal()
  
base_plot3

```


### Check for influential points
 
Look for pairs that significantly deviate.
```{r}
# General mean accuracy for each pair:
pair_mean_acc <- ddply(data_all, c("subject_nr"), 
                        summarise,
                        prop_cor=mean(correct, na.rm=FALSE),
                        prop_any_cor=mean(any_correct, na.rm=FALSE))
#Overall mean accuracy of participants & sd
overall_mean_acc <- data.table(MeanAcc = round(mean(pair_mean_acc$prop_cor), 2), SDAcc =round(sd(pair_mean_acc$prop_cor), 2)) 


#scatterplot for the different pairs (possible outliers) 
pair_mean_plot<- ggplot(data=pair_mean_acc,
                       aes(x=subject_nr, y= prop_cor)) +
                       geom_point( color="blueviolet") +
                       labs(title="Mean matching accuracy per pair",
                       x="pairs", y = "mean accuracy") +
                       coord_cartesian(ylim=c(0.0, 1))+
                       geom_hline(aes(yintercept = 0.644, linetype="Mean = .64"), 
                                  color = "red", size=0.7, show.legend = TRUE)+
  
                       theme_minimal()
pair_mean_plot


# Checks - Removes outliers (> 3 SD)   

by(data_all,data_all$subject_nr, 
    function(z) z$correct[abs(z$correct-mean(z$correct))< 3*sd(z$correct)]) # none



```


### Other insights

Estimate the mean matching accuracy for each pair by block & condition
```{r}
pair_descr_dat <- ddply(data_all, c("subject_nr", "load_condition", "stim_type", "block"), 
                 summarise,
                 correct_prop=mean(correct),
                 se_cor_prop=se(correct),
                 correct_any_prop=mean(any_correct),
                 se_cor_any_prop=se(any_correct))
pair_descr_dat



# Spaghetti plot between blocks for each pair + mean 

block_mean_plot<- ggplot(data=pair_descr_dat,
                       aes(x=as.factor(block), y= correct_prop, group=subject_nr,
                           colour=as.factor(subject_nr))) +
                geom_point() +
                geom_line()+
                theme(legend.position = "none")+
                stat_summary(fun=mean,geom="line",lwd=2,aes(group=1))+
                labs(title="Coordination performance for each pair by block",
                     x="block", y = "Coordination Index")
 # facet_wrap(~ stim_type + load_condition)  # They only show one observation..Why? Remake.
  # facet_wrap(~ load_condition)
                
block_mean_plot
```

This spaghetti plot shows a general upward trend moving from block 1 to block 2, implying that subjs become better by time. However, we can also see a lot of individual differences. 

### Mixed-effects logistic regression GLMER:
Glemrs are used to binary outcome variables. Log odds of the outcomes 
are modeled as a linear combination of the predictor variables 
when data have both fixed and random effects.

\Note {Odds (more technically the odds of success) is defined as probability of success/probability of failure
Log odds is the logarithm of the odds.
Conversion to log odds results in symmetry around zero, which is easier for analysis}



##### Assumptions
1. random effects intercepts and slopes are normally distributed.
2. relationship between  the numeric predictors to the parameter of interest, via logit function
3. Appropriate estimation of variance


###### 1. Glmer with block
```{r}
# Note: 
# parameter optimization = selection of parameter values (= weights+biases), 
# which are optimal in some desired sense 


#Null Model
null_model <- glmer(correct ~ stim_type + (1 |subject_nr),
                data=data_all, 
                family="binomial", 
                control=glmerControl(optimizer = "bobyqa"))

summary(null_model)

data_all[, load_condition := relevel(load_condition, "low")] 

# Reduced Model
reduced_model <- glmer(correct ~ stim_type + block + (1 |subject_nr),
                    data=data_all, 
                    family="binomial", 
                    control=glmerControl(optimizer = "bobyqa"))
summary(reduced_model)

# Comparison A
anova(null_model, reduced_model)

#Full Model
full_model <- glmer(correct ~ stim_type + block + load_condition + (1|subject_nr),
                    data=data_all, 
                    family="binomial", 
                    control=glmerControl(optimizer = "bobyqa"))

summary(full_model)

#Comparison B
anova(full_model, reduced_model)


# Interaction btw stim * load
int_model1 <- glmer(correct ~ stim_type + block + load_condition + stim_type:load_condition +
                       (1|subject_nr),
                     data=data_all, 
                     family="binomial", 
                     control=glmerControl(optimizer = "bobyqa"))

# Comparison C
anova(int_model1, full_model) #interaction not significant


# interaction btw stim * block 
int_model2 <- glmer(correct ~ stim_type + block + load_condition + stim_type:block +
                       (1|subject_nr),
                     data=data_all,
                     family="binomial",
                     control=glmerControl(optimizer = "bobyqa"))
summary(int_model2)  

# Comparison D
anova(int_model2, full_model) # NOT SIGNIFICANT

#Interaction btw load * block
int_model3 <- glmer(correct ~ stim_type + block + load_condition + load_condition:block +
                      (1|subject_nr),
                    data=data_all,
                    family="binomial",
                    control=glmerControl(optimizer = "bobyqa"))
summary(int_model3)  

# Comparison E
anova(int_model3, full_model)

# 3way interaction stim*load*block

int_model4 <- glmer(correct ~ stim_type + block + load_condition + stim_type:load_condition:block +
                       (1|subject_nr),
                     data=data_all, 
                     family="binomial", 
                     control=glmerControl(optimizer = "bobyqa"))
summary(int_model4)

# Comparison F
anova(int_model4, int_model3)  # significant, but warning on deficient matrix; dropping columns (too complex - not supported?) 

```

Plot Predicted probabilities from the model following [example](https://cran.r-project.org/web/packages/ggeffects/vignettes/practical_logisticmixedmodel.html) 
by Daniel Lüdecke

```{r}
ggpredict(null_model, "stim_type")
marginal_effects_fullmodel <- as.data.table(ggpredict(full_model, c("stim_type", "load_condition", "block")))


# plot using the pipe (!!!!) : Check this
me <- ggpredict(full_model, "stim_type")
plot(me)

marg_effects_fullmd <- ggpredict(full_model, c("stim_type", "load_condition", "block")) %>% plot(color = "Set1")
marg_effects_fullmd
#marg_effects_int_md <- ggpredict(int_model4, c("stim_type", "load_condition", "block")) %>% plot(color = "Set1")



```

###### 2. Glmer without block

```{r}
nll_model <- glmer(correct ~ stim_type + (1 |subject_nr),
                    data=data_all, 
                    family="binomial", 
                    control=glmerControl(optimizer = "bobyqa"))

summary(nll_model)

data_all[, load_condition := relevel(load_condition, "high")] 


# Full model
fll_model <- glmer(correct ~ stim_type + load_condition + (1|subject_nr),
                    data=data_all, 
                    family="binomial", 
                    control=glmerControl(optimizer = "bobyqa"))

summary(fll_model)

anova(fll_model, nll_model)


# Interaction btw stim * load
intrct_model <- glmer(correct ~ stim_type + load_condition + stim_type*load_condition + (1|subject_nr),
                      data=data_all, 
                      family="binomial", 
                      control=glmerControl(optimizer = "bobyqa"))

summary(intrct_model)

#comparison b
anova(fll_model, intrct_model) #not significant 

```


### Linear Mixe Models Analysis
#### Data preparation

Prepare the data so as to be continuous to use them in the models. 

1. Basic Structure: take the mean of each pair within each block

```{r}
data_all[, block:=droplevels(block)]
data_all[, stim_type:=droplevels(stim_type)]


blocked_data <- data.table(data_all)[,.(subject_nr, stim_type, load_condition, correct, trial, block)]
blocked_data[,`:=`(matching_freq=round(mean(correct),2), se_mf= round(se(correct),2)), by= .(subject_nr, block)]

blocked_data_uni<- blocked_data %>% distinct(subject_nr, block, .keep_all = TRUE)
```

2. Create bins and split the data into 10 bins per block for each pair of participants

```{r}


# define bin width
bin_width = 10

# cut the data
blocked_data[,`:=`(bin = cut(trial, breaks = seq(1, nrow(blocked_data)+1, by=bin_width), right=FALSE))]

# Create a data table with binned data & drop the overall matching frequency & se columns
binned_data <- blocked_data
binned_data[,matching_freq:=NULL]
binned_data[,se_mf:=NULL]
binned_data[,bin:= as.numeric(bin)]


# find the matching frequency within each pair bin
binned_data[,`:=`(matching_freq=round(mean(correct),2), se= round(se(correct),2)), by= .(subject_nr, bin)]
binned_data <- binned_data %>% distinct(subject_nr, bin, .keep_all = TRUE)

```





#### 1.a. LMM in the binned data (block included)

```{r}
#null model 1 (wihtout factor of interest)
nullmdl1<-lmer(matching_freq ~ stim_type + (1|subject_nr) , data = binned_data, REML = FALSE)
summary (nullmdl1)

#reduced model 1 (with block)
reducedmdl<-lmer(matching_freq ~ stim_type + block + (1|subject_nr) , data = binned_data, REML = FALSE)
summary(reducedmdl)

#comparison A
anova(nullmdl1, reducedmdl) #significant but higher AIC value

#full model (with cognitive _load)
fullmdl<-lmer(matching_freq ~ stim_type + load_condition + (1|subject_nr) , data = binned_data, REML = FALSE)
summary(fullmdl)

#comparison B
anova(nullmdl1, fullmdl)


# interaction model 1 (stim & load)
intmdl1<-lmer(matching_freq ~ stim_type + load_condition + stim_type*load_condition + 
                 (1|subject_nr) , data = binned_data, REML = FALSE)
summary(intmdl1)

#comparison C
anova(fullmdl, intmdl1)   #not significant --> DROP   #but low AIC


#full model 2 (adding block)
fullmdl2<-lmer(matching_freq ~ stim_type + load_condition + block + (1|subject_nr) , 
               data = binned_data, REML = FALSE)
summary(fullmdl2)


#comparison D
anova(fullmdl2, reducedmdl)
anova(fullmdl, fullmdl2) #significant



#interaction model 4 (stim* load)
intmdl4<-lmer(matching_freq ~ stim_type + load_condition + block + load_condition * stim_type + 
                 (1|subject_nr) , data = binned_data, REML = FALSE)
summary(intmdl4)

#comparison E
anova(intmdl4, fullmdl2) # not sign



#interaction model 2 ( stim * block )
intmdl2<-lmer(matching_freq ~ stim_type + load_condition + block + stim_type * block + 
                 (1|subject_nr) , data = binned_data, REML = FALSE)
summary(intmdl2)

#comparison F
anova(fullmdl2, intmdl2) # Not significant--> DROP


#interaction model 5 (interaction load*block)
int_mdl3<-lmer(matching_freq ~ stim_type + load_condition + block + load_condition * block + 
                 (1|subject_nr) , data = binned_data, REML = FALSE)
summary(int_mdl3)

#comparison G
anova(fullmdl2, int_mdl3) # significant --> there is an effect of time in load



# 3-way interaction
intmdl5<-lmer(matching_freq ~ stim_type + load_condition + block + stim_type*load_condition * block + 
                 (1|subject_nr) , data = binned_data, REML = FALSE)
summary(intmdl5)

#comparison J
anova(int_mdl3, intmdl5)  # almost significant ~

```

#### 1.b. LMM in the binned data with bin as predictor (block included)

```{r}

# careful: bin should be numeric, not factor!

n_mdl<-lmer(matching_freq ~ stim_type + (1|subject_nr) , data = binned_data, REML = FALSE)
summary (n_mdl)



#reduced model (with bin)
r_mdl<-lmer(matching_freq ~ stim_type + bin + (1|subject_nr) , data = binned_data, REML = FALSE)
summary(r_mdl)

#comparison A
anova(n_mdl, r_mdl)

#full model 
f_mdl<-lmer(matching_freq ~ stim_type + bin + load_condition + (1|subject_nr) , data = binned_data, REML = FALSE)
summary(f_mdl)

#comparison B
anova(r_mdl, f_mdl)


#interaction 1
int1_mdl<-lmer(matching_freq ~ stim_type + bin + load_condition + stim_type*load_condition + (1|subject_nr) , data = binned_data, REML = FALSE)
summary(int1_mdl)

#comparison C
anova(int1_mdl, f_mdl)

#interaction 2
int2_mdl<-lmer(matching_freq ~ stim_type + bin + load_condition + bin*load_condition + (1|subject_nr) , data = binned_data, REML = FALSE)
summary(int2_mdl)

#comparison D
anova(int2_mdl, f_mdl)


#interaction 3-way
int3_mdl<-lmer(matching_freq ~ stim_type + bin + load_condition + bin*load_condition + bin*load_condition*stim_type + (1|subject_nr) , data = binned_data, REML = FALSE)
summary(int3_mdl)

#comparison E
anova(int3_mdl, int2_mdl)
```


#### 2.a. LMM in mean data 

```{r}
# data preparation 
lmm_data <- data.table(data_all)[,.(subject_nr, stim_type, load_condition, correct, trial, block)]
lmm_data[,`:=`(mean_correct=round(mean(correct),2), sd_mc= round(se(correct),2)), by= .(subject_nr, block)]

lmm_data<- lmm_data %>% distinct(subject_nr, block, .keep_all = TRUE)
# Models

#nullmodel
nullmodel<-lmer(mean_correct ~ stim_type + (1|subject_nr) , data = lmm_data, REML = FALSE)
summary (nullmodel)

#reducedmodel
reducedmodel<- lmer(mean_correct ~ stim_type + block + (1|subject_nr) , data = lmm_data, REML = FALSE)
summary (reducedmodel)

#comparison A
anova(reducedmodel, nullmodel)

#fullmodel
fullmodel <- lmer(mean_correct ~ stim_type + block + load_condition + (1|subject_nr) , data = lmm_data, REML = FALSE)
summary (fullmodel)


#comparison B
anova(fullmodel, reducedmodel)
# anova(fullmodel, nullmodel)

#intmodel1   
interaction_model <-lmer(mean_correct ~ stim_type + block + load_condition + stim_type*block + (1|subject_nr) , data = lmm_data, REML = FALSE)
summary (interaction_model)

#comparison C
anova(interaction_model, fullmodel) #not sign

#interaction model 2
interaction_model2 <-lmer(mean_correct ~ stim_type + block + load_condition + stim_type*load_condition + (1|subject_nr) , data = lmm_data, REML = FALSE)
summary (interaction_model2)

#comparison D
anova(interaction_model2, fullmodel) #not sign

#interaction model 3
interaction_model3 <-lmer(mean_correct ~ stim_type + block + load_condition + block*load_condition + (1|subject_nr) , data = lmm_data, REML = FALSE)
summary (interaction_model3)

#comparison E
anova(interaction_model3, fullmodel)

#interaction model 4 : 3way
interaction_model4 <-lmer(mean_correct ~ stim_type + block + load_condition + block*load_condition*stim_type + (1|subject_nr) , data = lmm_data, REML = FALSE)
summary (interaction_model4)

#comparison F
anova(interaction_model3, interaction_model4) #not sing
anova(interaction_model4, fullmodel) # not sign

```

#### 2.b. LMM in mean data without block

```{r}
#nullmodel
null_mdl<-lmer(mean_correct ~ stim_type + (1|subject_nr) , data = lmm_data, REML = FALSE)
summary (null_mdl)


#fullmodel
full_mdl <- lmer(mean_correct ~ stim_type + load_condition + (1|subject_nr) , data = lmm_data, REML = FALSE)
summary (full_mdl)


# a boxplot:
# the shape of the distribution, its central value, and its variability
boxplot(mean_correct ~ stim_type + load_condition, data= lmm_data, boxfill = lmm_data$load_condition)

boxplot.lmm_data<- ggplot(lmm_data, aes(stim_type, mean_correct, fill = load_condition)) + 
                    geom_boxplot()+
                    scale_fill_manual(values=c("low" = "darkslateblue", "high" = "tomato3"))+
                    theme_minimal()+
                    labs(title="Mean matching accuracy per condition",x="Stimulus Tupe",
                         y = "Mean Accuracy", fill = "Load Condition")+
                    theme(legend.justification = "center", plot.title = element_text(hjust = 0))

#comparison a
anova(full_mdl, null_mdl) #sing (better BIC but not AIC)


#intmodel1   
intrct_mdl <-lmer(mean_correct ~ stim_type + load_condition + stim_type*load_condition + (1|subject_nr) , data = lmm_data, REML = FALSE)
summary (intrct_mdl)

#comparison b
anova(intrct_mdl, full_mdl) #not significant (but better AIC &BIC)

```


#### 2.c. LMM-Checking Assumptions 
1. Normality of model residuals
2. Linearity & homoscedasticity

For Binned data with bin as a predictor 
```{r}
# Normality : 
# a. QQ-plot
qqnorm(residuals(int2_mdl))
qqline(residuals(int2_mdl), col = "steelblue", lwd = 2)
# b. Histogram 
hist(residuals(int2_mdl))

# Linearity & Hmscdasticity:
plot(fitted(int2_mdl),residuals(int2_mdl))
```

[x] There are no obvious violations of the assumptions 








# Folded Data: Collapsed block
If we would be interested to see how learning evolves or the actual effect and resetting of the block change, we shall continue in the above away. However, we currently just want to see the effects of the different conditions. Therefore, we will collapse the blocks. 


```{r}
#set the order of the dataset
setcolorder(data_all, c("subject_nr", "trial", "load_condition", "stim_type", "correct"))

# clear from unwanted columns
data_all[,(6:12):= NULL]

#collapse blocks
first_fold <- data_all[trial <= 90]
second_fold <- data_all[trial > 90]
second_fold<- mutate(second_fold, trial = trial - 90)
data_folded <- rbind(first_fold, second_fold)

```

Create bins and calculate the mean. 

```{r}
# define bin width
bin_width = 10

# cut the data
data_folded[,`:=`(bin = cut(trial, breaks = seq(1, nrow(data_folded)+1, by=bin_width), right=FALSE))]

# Create a data table with binned data & drop the overall matching frequency & se columns
binned_fdata <- data_folded
binned_fdata[,bin:= as.numeric(bin)]

# find the matching frequency within each pair bin
binned_fdata[,`:=`(coord_indx= mean(correct), se= se(correct)), by= .(subject_nr, bin)]
binned_fdata <- binned_fdata %>% distinct(subject_nr, bin, .keep_all = TRUE)
```

## LMM in folded-binned data

```{r}
#intercept only model  
intercept_mdl<-lmer(coord_indx ~ 1 + (1|subject_nr) , data = binned_fdata, REML = FALSE)

#time model 
time_mdl<-lmer(coord_indx ~ bin + (1|subject_nr) , data = binned_fdata, REML = FALSE)


#model comparison
anova(intercept_mdl, time_mdl)

summary(time_mdl)


formatC(3.320e-02, digits = 4)
```

```{r}

#time model 
time_mdl<-lmer(coord_indx ~ bin + (1|subject_nr) , data = binned_fdata, REML = FALSE)

#reduced_model 
reduced_mdl<-lmer(coord_indx ~ bin + stim_type + (1|subject_nr) , data = binned_fdata, REML = FALSE)


#model comparison
anova(time_mdl, reduced_mdl)

summary(reduced_mdl)

```

```{r}
#time model 
time_mdl<-lmer(coord_indx ~ bin + (1|subject_nr) , data = binned_fdata, REML = FALSE)

#reduced_model 
full_mdl<-lmer(coord_indx ~ bin + load_condition + (1|subject_nr) , data = binned_fdata, REML = FALSE)


#model comparison
anova(time_mdl, full_mdl)

summary(full_mdl)

```




Checking Assumptions 
```{r}
# Normality : 
# a. QQ-plot
qqnorm(residuals(full_mdl))
qqline(residuals(full_mdl), col = "steelblue", lwd = 2)
# b. Histogram 
hist(residuals(full_mdl))

# Linearity & Hmscdasticity:
plot(fitted(full_mdl),residuals(full_mdl))
```
```{r}

#reduced_model 
full_mdl<-lmer(coord_indx ~ bin + load_condition + (1|subject_nr) , data = binned_fdata, REML = FALSE)

#time model 
interaction_mdl<-lmer(coord_indx ~ bin*load_condition + (1|subject_nr) , data = binned_fdata, REML = FALSE)



#model comparison
anova(interaction_mdl, full_mdl)

summary(interaction_mdl)

```


### Presenting the data

#### Plotting the data

1. How much does each predictor affects our DV over time? 
Plot the coordination index (y) over the binned data (x) for stimulus type & cognitive load
```{r, Coordinating performance over time}
# Plot binned_data as a function of time
bin_plot<- ggplot(binned_fdata, aes(x = bin, y = coord_indx)) + 
  geom_smooth()+
  geom_point(position = "jitter", alpha = .3)+
  # geom_vline(aes(xintercept = 10, linetype = "dashed"))+
  # geom_point(aes(x = bin, y = matching_freq)+
  # scale_fill_manual(values= "blue") +
  # scale_linetype_manual(name= "Block Change", values = 9) +
  labs(x = "Time (bins)", y = "Coordination Index" 
       ) + 
  theme_minimal()+
  expand_limits(y=c(0, 1))

title = "Coordinating performance over time"


bin_plot
```


```{r}
# Plot binned_data + load condition
load_plot <- ggplot(binned_fdata, aes(x = bin, y = coord_indx, colour= load_condition)) + 
              geom_smooth()+
              geom_point(position = "jitter", alpha = .3)+
              # geom_vline(aes(xintercept = 10, linetype = "dashed"))+
              scale_color_manual(values=c("low" = "darkslateblue", "high" = "tomato3"))+              
              labs(x = "Time (bins)", y = "Coordination Index" ) + 
            
              # scale_linetype_manual(name= "Block Change", values = 9) +
              expand_limits(y=c(0, 1))+
              guides(col=guide_legend("WM load")) +
              theme_minimal()
 
   
title = "Mean Matching accuracy by cognitive load over time"             
load_plot + theme(legend.position="bottom")

```

```{r}

# Plot binned_data + stim_type
stim_type_plot<- ggplot(binned_fdata) + 
                  geom_smooth(aes(x = bin, y = coord_indx, colour= stim_type))+
                  # geom_vline(aes(xintercept = 10, linetype = "dashed"))+
                  # geom_point(aes(x = bin, y = matching_freq, colour= stim_type))+ # each point represents the mean #acc of each pair in x bin.
                  scale_color_manual(values=c("color" = "darkslateblue", "shape" = "tomato3"))+
                  # scale_linetype_manual(name= "Block Change", values = 9) +
                  labs(x = "Trial bin", y = "Mean Accuracy", 
                       title = "Mean Matching accuracy by stimulus type over time") + 
                  theme_minimal()+
                  expand_limits(y=c(0, 1))

stim_type_plot
```

```{r}
# Plot binned_data + load condition
load_plot <- ggplot(binned_fdata) + 
              geom_smooth(aes(x = bin, y = coord_indx, colour= load_condition))+
              # geom_vline(aes(xintercept = 10, linetype = "dashed"))+
              scale_color_manual(values=c("low" = "darkslateblue", "high" = "tomato3"))+              
   labs(x = "Trial bin", y = "Mean Accuracy", 
                   title = "Mean Matching accuracy by cognitive load over time") + 
              # scale_linetype_manual(name= "Block Change", values = 9) +
              expand_limits(y=c(0, 1))+
              theme_minimal()+
              facet_grid(~ stim_type)
load_plot

```

Alternative
```{r}
# Plot model estimates WITH data---------------------
# Step 1: Save the effect size estimates into a data.frame

# effect function. term= the fixed effect you want to get data on,
# mod= name of your model.

effects_int_model <- effects::effect(term= "bin", mod= int2_mdl)
summary(effects_int_model)

# Save the effects values as a df:
x_int_model <- as.data.frame(effects_int_model)


#Step 2: Use the effects value df (created above) to plot the estimates

#1 Create empty plot
bin_lmmplot <- ggplot() + 

#2 Add geom_points() from the DATA: bin data on the x axis (independent va= c.urchinden) and matching data on the y-axis (response var)
  # geom_point(data=binned_data, aes(bin, matching_freq)) + 
  
#3 Add geom_point for the MODEL estimates (data= x_urchi here, this is the dataset you created in the above chunk). We will change the color so they are distinguishable from the data
   geom_point(data=x_int_model, aes(x=bin, y=fit), color="blue") +
  
#4 Add geom_line for the MODEL estimates. Change the color to match the estimate points (ie whatever color you chose for step3)
  geom_line(data=x_int_model, aes(x=bin, y=fit), color="blue") +
#5 Add geom_ribbon that has the CI limits for the model estimates
  geom_ribbon(data= x_int_model, aes(x=bin, ymin=lower, ymax=upper), alpha= 0.3, fill="blue") +
#6 Edit the labels as you see fit!
  labs(x = "Time (trial bin)", y = "Coordination Index", 
       title = "Coordination performance over time") + 
  geom_vline(aes(xintercept = 10, linetype = "dashed"))+
  scale_linetype_manual(name= "Block Change", values = 9)+
  theme_minimal()+
  theme(legend.key.size = unit(0.2, "cm"))



bin_lmmplot

```




2. Create a table of the model estimates
([example](https://lmudge13.github.io/sample_code/mixed_effects.html))

```{r}
int2_mdl_table<- sjPlot::tab_model(int2_mdl, 
                  show.re.var= TRUE, 
                  pred.labels =c("(Intercept)", "Stimulus Type (shape)", "Trial Bin", "Cognitive Load (low)", 
                                 "Trial Bin * Cognitive Load (low)"),
                  dv.labels= "Effects of Predictors on Coordination Index \nof the Interaction model",
                  file="interaction_table.html")


```

### The End


### Change of plots to reporting RAW DATA
https://stackoverflow.com/questions/52778386/how-to-plot-raw-data-but-use-predicted-values-for-line-fit-in-ggplot2-r